Formalizing Stack Safety as a Security Property\ifcameraready\else\vspace{-0.75cm}\fi

### 2023-05-24 submission5/core.tex

To our knowledge, the only other line of work that aims to rigorously characterize the
security of the stack is the StkTokens-Cerise family of CHERI-enforced secure calling
conventions \cite{SkorstengaardLocal, SkorstengaardSTKJFP, Georges22:TempsDesCerises}.
%
The authors define stack safety as overlay semantics and related stack
safety properties, phrased in terms of logical relations instead of trace
properties.
%
Originally, they describe ``local state encapsulation''~\cite{SkorstengaardSTKJFP}
in terms of integrity only (but it has confidentiality, equivalent
to \(\clri\) {\em and} \(\clrc\)). Their latest
paper \cite{Georges22:TempsDesCerises} was inspired by the properties presented
in this paper to extend their formalism to include confidentiality. When
checking if our properties applied to their old calling convention, they noted that
it did not enforce \(\clec\), and made sure that their new version
would in addition to building it into their formalism
\cite{Georges22:personalcommunication}. This demonstrates the benefit of our
choice to explicitly state properties in security terms: specifying security
is hard, and when the spec takes the form of a ``correct by
construction'' machine, it is easy to neglect a non-obvious security
requirement.

>>>>

To our knowledge, the only other line of work that aims to rigorously characterize the
security of the stack is the StkTokens-Cerise family of CHERI-enforced secure calling
conventions \cite{SkorstengaardLocal, SkorstengaardSTKJFP, Georges22:TempsDesCerises}.
%
The authors define stack safety as overlay semantics and related stack
safety properties, phrased in terms of logical relations instead of trace
properties.
%
Originally, they define an informal notion of stack safety as the combination of WBCF
and ``local state encapsulation''~\cite{SkorstengaardSTKJFP},
and describe the latter
in terms of integrity only (but it has confidentiality, equivalent
to \(\clri\) {\em and} \(\clrc\)).
%
StkTokens \cite{SkorstengaardSTKJFP} makes this conception of stack safety
explicit through an overlay semantics
%(that internalizes the semantics of the calling convention and is proved fully
%abstract w.r.t. the concrete machine executing the actual calling convention).
%This overlay manipulates an abstract call stack whose elements are frames. A
%function call creates a new stack frame off of a capability representing the
%available stack space, and a function return merges the corresponding frame
%back into the stack capability. It is assumed that components do not leave any
%capabilities on the stack when they return.
which (1) on call mints new a stack frame from a capability representing the
available stack space, and (2) on return merges the current frame back into the
stack capability, under the assumption that there are no capabilities left on
the stack.

Their latest
paper \cite{Georges22:TempsDesCerises} was inspired by the properties presented
in this paper to extend their formalism to include confidentiality. When
checking if our properties applied to their old calling convention, they noted that
it did not enforce \(\clec\), and made sure that their new version
would in addition to building it into their formalism.\footnote{A. L. Georges,
personal communication.}
%\cite{Georges22:personalcommunication}.
%
To do so, they redesign the overlay semantics to actually pop stack frames on
return and have them disappear from the stack.
%
This demonstrates the benefit of our
choice to explicitly state properties in security terms: specifying security
is hard, and when the spec takes the form of a ``correct by
construction'' machine, it is easy to neglect a non-obvious security
requirement.

% \cite{Georges22:TempsDesCerises} revisits this design and modifies the
% overlay in an interesting way to actually pop stack frames on return and have
% them disappear from the stack rather than be merged back into it. It thus
% realizes callee confidentiality (and no dangling stack pointers).
